Verification of the CVM algorithm with a new Recursive Analysis Technique

### 2025-01-25 isabelle/CVM_Subsample/document/appendix.tex
Merge Utils_Basic/PMF.   + Minor improvments.

\paragraph{Notation:} For the bernoulli probability space, over the set $\{0,1\}$ we'll write 
$\mathrm{Ber}(p)$, i.e., $P_{\mathrm{Ber}(p)}(\{1\}) = p$. $I(P)$ is the indicator function for a 
predicate $P$, i.e., $I(\mathrm{true}) = 1$ and $I(\mathrm{false}) = 0$.

@@

\subsection{Loop Invariant}
After these preliminiaries, we can go to the main proof, whose core is an probabilistic loop
invariant for Algorithm~\ref{alg:cvm_abs} that can be verified inductively.

>>>>

\paragraph{Notation:} For a finite set $S$, the probability space of uniformly sampling from the set
is denoted by $U(S)$, i.e., for each $s \in S$ we have $\prob_{U(S)}({s}) = |S|^{-1}$.
For the bernoulli probability space, over the set $\{0,1\}$ we'll write $\mathrm{Ber}(p)$, i.e.,
$P_{\mathrm{Ber}(p)}(\{1\}) = p$. $I(P)$ is the indicator function for a predicate $P$, i.e.,
$I(\mathrm{true}) = 1$ and $I(\mathrm{false}) = 0$.

@@

\subsection{Loop Invariant}
After these preliminiaries, we can go to the main proof, whose core is a probabilistic loop
invariant for Algorithm~\ref{alg:cvm_abs} that can be verified inductively.
